---
title: "biota_data"
vignette: >
  %\VignetteIndexEntry{biota_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

Data on sampled biota, if relevant.

-   Link to ecotox db
-   Plan to use EoL or wikispecies in future
-   [Test link to samples data](samples_data.html)

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_biota_tibble()
```

## Variables

# Sample ID - String, free, mandatory
`SAMPLE_ID`

<!-- Unique identifier linking to the samples table. Foreign key for measurements. -->

# Site Code - String, free, mandatory
`SITE_CODE`

<!-- Code identifying the sampling location. Foreign key for sites. -->

# Parameter Name - String, free, mandatory
`PARAMETER_NAME`

<!-- Name of the measured parameter or stressor. Foreign key for parameters. -->

# Environ Compartment - String, controlled, mandatory
`ENVIRON_COMPARTMENT`

<!-- Broad environmental compartment category. Inherited from the samples table. -->

```{r}
#| label: environ_compartment

environ_compartments_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_vocabulary() output. -->

# Environ Compartment Sub - String, controlled, mandatory
`ENVIRON_COMPARTMENT_SUB`

<!-- Specific sub-category of the environmental compartment. Inherited from the samples table. -->

```{r}
#| label: environ_compartment_sub

environ_compartments_sub_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_sub_vocabulary() output. -->

# Measured Category - String, controlled, mandatory
`MEASURED_CATEGORY`

<!-- Category indicating measurement context. Inherited from the samples table. -->

```{r}
#| label: measured_category

measured_categories_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from measured_categories_vocabulary() output. -->

# Sampling Date - String, free, mandatory
`SAMPLING_DATE`

<!-- Date when the biological sample was collected. Inherited from the samples table. -->

# Subsample - String, free, mandatory
`SUBSAMPLE`

<!-- Identifier for subsample or replicate. Inherited from the samples table. -->

# Species Group - String, controlled, mandatory
`SPECIES_GROUP`

<!-- Taxonomic group classification, e.g., Fish, Molluscs, Plants. -->

```{r}
#| label: species_group

species_groups_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from species_groups_vocabulary() output. -->

# Sample Species - String, controlled, mandatory
`SAMPLE_SPECIES`

<!-- Scientific binomial name of the sampled species. -->

```{r}
#| label: sample_species

species_names_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from species_names_vocabulary() output. -->

# Sample Tissue - String, controlled, mandatory
`SAMPLE_TISSUE`

<!-- Type of biological tissue sampled. -->

```{r}
#| label: sample_tissue

tissue_types_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from tissue_types_vocabulary() output. -->

# Sample Species Lifestage - String, controlled, mandatory
`SAMPLE_SPECIES_LIFESTAGE`

<!-- Life stage of the organism at sampling. -->

```{r}
#| label: sample_species_lifestage

lifestage_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from lifestage_vocabulary() output. -->

# Sample Species Gender - String, controlled, mandatory
`SAMPLE_SPECIES_GENDER`

<!-- Gender or sex of the sampled organism. -->

```{r}
#| label: sample_species_gender

gender_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from gender_vocabulary() output. -->

# Biota Comment - String, free, optional
`BIOTA_COMMENT`

<!-- Additional notes or comments about the biological sample. -->
