---
title: "campaign_data"
vignette: >
  %\VignetteIndexEntry{campaign_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

**Campaign data** is intended to track social and institutional factors behind a sample that are not otherwise captured by citations/references. It's a mess, and includes a bunch of fields that it probably shouldn't.

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_campaign_tibble()
```

## Variables

# Campaign Name Short - String, free, mandatory
`CAMPAIGN_NAME_SHORT`

<!-- Short identifier for the campaign. -->

# Campaign Name - String, free, mandatory
`CAMPAIGN_NAME`

<!-- Full descriptive name of the campaign. -->

# Campaign Start Date - Date, free, mandatory
`CAMPAIGN_START_DATE`

<!-- Date when campaign sampling began. -->

# Campaign End Date - Date, free, optional
`CAMPAIGN_END_DATE`

<!-- Date when campaign sampling ended. May be left blank if the campaign is ongoing or the end date is unknown. -->

# Organisation - String, free, mandatory
`ORGANISATION`

<!-- Organisation responsible for the campaign. -->

# Entered By - String, free, mandatory
`ENTERED_BY`

<!-- Person or entity who entered the data. -->

# Entered Date - Date, free, mandatory
`ENTERED_DATE`

<!-- Date when the data was entered into the system. -->

# Campaign Comment - String, free, optional
`CAMPAIGN_COMMENT`

<!-- Additional notes or comments about the campaign. -->
