---
title: "Measurements Table"
vignette: >
  %\VignetteIndexEntry{measurements_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_measurements_tibble()
```

## Variables

# Site Code - String, free, mandatory
`SITE_CODE`

<!-- Code identifying the sampling location. -->

# Parameter Name - String, free, mandatory
`PARAMETER_NAME`

<!-- Name of the measured parameter. Foreign key for parameters. -->

# Sampling Date - String, free, mandatory
`SAMPLING_DATE`

<!-- Date of sample collection. -->

# Environ Compartment Sub - String, controlled, mandatory
`ENVIRON_COMPARTMENT_SUB`

<!-- Specific environmental sub-compartment. -->

```{r}
#| label: environ_compartment_sub

environ_compartments_sub_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_sub_vocabulary() output. -->

# Subsample - String, free, mandatory
`SUBSAMPLE`

<!-- Subsample identifier. -->

# Measured Flag - String, controlled, mandatory
`MEASURED_FLAG`

<!-- Quality flag for the measurement (e.g., < LOQ, < LOD). -->

```{r}
#| label: measured_flag

measured_flags_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from measured_flags_vocabulary() output. -->

# Measured Value - Numeric, free, mandatory
`MEASURED_VALUE`

<!-- Numeric value of the measurement. -->

# Uncertainty Type - String, controlled, mandatory
`UNCERTAINTY_TYPE`

<!-- Type of uncertainty or variability metric. -->

```{r}
#| label: uncertainty_type

uncertainty_types_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from uncertainty_types_vocabulary() output. -->

# Uncertainty Upper - Numeric, free, mandatory
`UNCERTAINTY_UPPER`

<!-- Upper bound of uncertainty. -->

# Uncertainty Lower - Numeric, free, mandatory
`UNCERTAINTY_LOWER`

<!-- Lower bound of uncertainty. -->

# Measured Unit - String, controlled, mandatory
`MEASURED_UNIT`

<!-- Unit of measurement. -->

```{r}
#| label: measured_unit

parameter_unit_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from parameter_unit_vocabulary() output. -->

# Measured N - Numeric, free, mandatory
`MEASURED_N`

<!-- Number of replicates or observations. -->

# LOQ Value - Numeric, free, mandatory
`LOQ_VALUE`

<!-- Limit of quantification value. -->

# LOQ Unit - String, controlled, mandatory
`LOQ_UNIT`

<!-- Unit for the limit of quantification. -->

```{r}
#| label: loq_unit

parameter_unit_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from parameter_unit_vocabulary() output. -->

# LOD Value - Numeric, free, mandatory
`LOD_VALUE`

<!-- Limit of detection value. -->

# LOD Unit - String, controlled, mandatory
`LOD_UNIT`

<!-- Unit for the limit of detection. -->

```{r}
#| label: lod_unit

parameter_unit_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from parameter_unit_vocabulary() output. -->

# Sampling Protocol - String, controlled, mandatory
`SAMPLING_PROTOCOL`

<!-- Protocol used for sample collection. Foreign key for methods. -->

```{r}
#| label: sampling_protocol

sampling_protocols_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from sampling_protocols_vocabulary() output. -->

# Extraction Protocol - String, controlled, mandatory
`EXTRACTION_PROTOCOL`

<!-- Protocol used for sample extraction. Foreign key for methods. -->

```{r}
#| label: extraction_protocol

extraction_protocols_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from extraction_protocols_vocabulary() output. -->

# Fractionation Protocol - String, controlled, mandatory
`FRACTIONATION_PROTOCOL`

<!-- Protocol used for sample fractionation. Foreign key for methods. -->

```{r}
#| label: fractionation_protocol

fractionation_protocols_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from fractionation_protocols_vocabulary() output. -->

# Analytical Protocol - String, controlled, mandatory
`ANALYTICAL_PROTOCOL`

<!-- Protocol used for analysis. Foreign key for methods. -->

```{r}
#| label: analytical_protocol

analytical_protocols_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from analytical_protocols_vocabulary() output. -->

# Reference ID - String, free, mandatory
`REFERENCE_ID`

<!-- Reference identifier for the data source. Foreign key for references. -->

# Sample ID - String, free, mandatory
`SAMPLE_ID`

<!-- Unique sample identifier. -->

# Campaign Name Short - String, free, mandatory
`CAMPAIGN_NAME_SHORT`

<!-- Short name of the associated campaign. -->

# Environ Compartment - String, controlled, mandatory
`ENVIRON_COMPARTMENT`

<!-- Broad environmental compartment. -->

```{r}
#| label: environ_compartment

environ_compartments_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_vocabulary() output. -->

# Parameter Type - String, controlled, mandatory
`PARAMETER_TYPE`

<!-- Classification of the parameter. -->

```{r}
#| label: parameter_type

parameter_types_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from parameter_types_vocabulary() output. -->

# Measured Type - String, controlled, mandatory
`MEASURED_TYPE`

<!-- Type of measurement. -->

```{r}
#| label: measured_type

measured_types_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from measured_types_vocabulary() output. -->

# Measurement Comment - String, free, optional
`MEASUREMENT_COMMENT`

<!-- Additional notes about the measurement. -->
