---
title: "Methods table"
vignette: >
  %\VignetteIndexEntry{methods_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

Really we should be using the Chemical Methods ontology here, but implementing it now will require a fair amount of structural redesign, so for now it's firmly in the todo category.

The Methods table is a metadata table that is transformed before being linked to the \[Measurements table\] {Measurements table}.

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_methods_tibble()
```

## Variables

# Protocol ID - String, free, mandatory
`PROTOCOL_ID`

<!-- Unique identifier for the protocol. Primary key. -->

# Campaign Name - String, free, mandatory
`CAMPAIGN_NAME`

<!-- Name of the campaign this protocol was used in. -->

# Protocol Category - String, free, mandatory
`PROTOCOL_CATEGORY`

<!-- Type of protocol (Sampling, Extraction, Fractionation, Analytical). -->

# Protocol Name - String, free, mandatory
`PROTOCOL_NAME`

<!-- Standardised name of the protocol. -->

# Protocol Comment - String, free, optional
`PROTOCOL_COMMENT`

<!-- Additional notes or details about the protocol. -->
