---
title: "references_data"
vignette: >
  %\VignetteIndexEntry{references_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_references_tibble()

reference_character_limits()
```

## Variables

# Reference ID - String, free, mandatory
`REFERENCE_ID`

<!-- Unique identifier for the reference. Primary key. -->

# Reference Type - String, free, mandatory
`REFERENCE_TYPE`

<!-- Type of publication (Journal Article, Report, Dataset, etc.). -->

# Data Source - String, free, mandatory
`DATA_SOURCE`

<!-- Source or database where the reference was obtained. -->

# Author - String, free, mandatory
`AUTHOR`

<!-- Author(s) of the reference. -->

# Title - String, free, mandatory
`TITLE`

<!-- Title of the publication or document. -->

# Year - Numeric, free, mandatory
`YEAR`

<!-- Publication year. -->

# Access Date - Date, free, mandatory
`ACCESS_DATE`

<!-- Date when the reference was accessed or retrieved. -->

# Periodical Journal - String, free, mandatory
`PERIODICAL_JOURNAL`

<!-- Name of the journal or periodical. -->

# Volume - Numeric, free, mandatory
`VOLUME`

<!-- Volume number of the journal. -->

# Issue - Numeric, free, mandatory
`ISSUE`

<!-- Issue number of the journal. -->

# Publisher - String, free, mandatory
`PUBLISHER`

<!-- Publisher of the document. -->

# Institution - String, free, mandatory
`INSTITUTION`

<!-- Institution associated with the publication. -->

# DOI - String, free, mandatory
`DOI`

<!-- Digital Object Identifier. -->

# URL - String, free, mandatory
`URL`

<!-- Web address for online access. -->

# ISBN ISSN - String, free, mandatory
`ISBN_ISSN`

<!-- ISBN or ISSN identifier. -->

# Edition - String, free, mandatory
`EDITION`

<!-- Edition of the publication. -->

# Document Number - String, free, mandatory
`DOCUMENT_NUMBER`

<!-- Document or report number. -->

# Ref Comment - String, free, optional
`REF_COMMENT`

<!-- Additional notes about the reference. -->
