---
title: "samples_data"
vignette: >
  %\VignetteIndexEntry{samples_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_samples_tibble()
```

## Variables

# Site Code - String, free, mandatory
`SITE_CODE`

<!-- Code identifying the sampling location. -->

# Site Name - String, free, mandatory
`SITE_NAME`

<!-- Descriptive name of the sampling site. -->

# Parameter Name - String, free, mandatory
`PARAMETER_NAME`

<!-- Name of the measured parameter. -->

# Parameter Type - String, controlled, mandatory
`PARAMETER_TYPE`

<!-- Classification of the parameter. -->

```{r}
#| label: parameter_type

parameter_types_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from parameter_types_vocabulary() output. -->

# Environ Compartment - String, controlled, mandatory
`ENVIRON_COMPARTMENT`

<!-- Environmental compartment defined as one of the earth's spheres (aquatic, atmospheric, etc.). -->

```{r}
#| label: environ_compartment

environ_compartments_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_vocabulary() output. -->

# Environ Compartment Sub - String, controlled, mandatory
`ENVIRON_COMPARTMENT_SUB`

<!-- Sub-divisions of environmental compartments into water body types, soil profile, etc. -->

```{r}
#| label: environ_compartment_sub

environ_compartments_sub_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from environ_compartments_sub_vocabulary() output. -->

# Measured Category - String, controlled, mandatory
`MEASURED_CATEGORY`

<!-- Measurement context category. -->

```{r}
#| label: measured_category

measured_categories_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from measured_categories_vocabulary() output. -->

# Sampling Date - String, free, mandatory
`SAMPLING_DATE`

<!-- Date of sample collection. -->

# Subsample - String, free, mandatory
`SUBSAMPLE`

<!-- Subsample or replicate identifier. -->

# Subsample ID - String, free, mandatory
`SUBSAMPLE_ID`

<!-- Unique identifier for the subsample. -->

# Sample ID - String, free, mandatory
`SAMPLE_ID`

<!-- Unique identifier for the sample. Key field. -->
