---
title: "sites_data"
vignette: >
  %\VignetteIndexEntry{sites_data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

# Introduction

```{r}
#| label: setup
library(eDataDRF)
```

```{r}
#| label: initialise

initialise_sites_tibble()
```

## Variables

# Site Code - String, free, mandatory
`SITE_CODE`

<!-- Unique code identifying the site. Primary key. -->

# Site Name - String, free, mandatory
`SITE_NAME`

<!-- Descriptive name of the sampling site. -->

# Site Geographic Feature - String, controlled, mandatory
`SITE_GEOGRAPHIC_FEATURE`

<!-- Broad geographic feature type of the sampling location. -->

```{r}
#| label: site_geographic_feature

geographic_features_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from geographic_features_vocabulary() output. -->

# Site Geographic Feature Sub - String, controlled, mandatory
`SITE_GEOGRAPHIC_FEATURE_SUB`

<!-- Specific sub-category of the geographic feature. -->

```{r}
#| label: site_geographic_feature_sub

geographic_features_sub_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from geographic_features_sub_vocabulary() output. -->

# Country ISO - String, controlled, mandatory
`COUNTRY_ISO`

<!-- ISO country code where the site is located. -->

```{r}
#| label: country_iso

countries_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from countries_vocabulary() output (ISO 3166-1 country names). -->

# Ocean IHO - String, controlled, mandatory
`OCEAN_IHO`

<!-- International Hydrographic Organisation ocean region. -->

```{r}
#| label: ocean_iho

areas_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from areas_vocabulary() output. -->

# Latitude - Numeric, free, mandatory
`LATITUDE`

<!-- Latitude coordinate in decimal degrees. -->

# Longitude - Numeric, free, mandatory
`LONGITUDE`

<!-- Longitude coordinate in decimal degrees. -->

# Site Coordinate System - String, controlled, mandatory
`SITE_COORDINATE_SYSTEM`

<!-- Coordinate reference system used for the site coordinates. -->

```{r}
#| label: site_coordinate_system

coordinate_systems_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from coordinate_systems_vocabulary() output. -->

# Altitude Value - Numeric, free, mandatory
`ALTITUDE_VALUE`

<!-- Elevation or depth value. -->

# Altitude Unit - String, controlled, mandatory
`ALTITUDE_UNIT`

<!-- Unit of measurement for the altitude value. -->

```{r}
#| label: altitude_unit

altitude_units_vocabulary()
```

## Controlled Vocabulary

<!-- Fill in from altitude_units_vocabulary() output. -->

# Entered By - String, free, mandatory
`ENTERED_BY`

<!-- Person or entity who entered the site data. -->

# Entered Date - String, free, mandatory
`ENTERED_DATE`

<!-- Date when the site data was entered. -->

# Site Comment - String, free, optional
`SITE_COMMENT`

<!-- Additional notes about the site. -->
